Clicks and Cliques

### 2018-12-19 papersoul.Rnw
tidy cluster.plot1 chunk

\begin{figure}[hbpt]
<<corplot, echo=FALSE, dependson=c('data'),cache=TRUE>>=
# With Census data we want to describe communities

@@

\begin{figure}[hbpt]
<<cluster.plot1, dependson='cluster',echo=FALSE,message=FALSE,warning=FALSE,warning=FALSE,fig.height=6.5>>=
lab <- c('Family','Refer','Perfect','Children','Leader','Proud', 'Lead. Int.','Talented','Job','Meet.People','
         5year.ahead', 'School','Reputation','5year.ago', 'Care', 'Senior','Economy','Satisfaction','Health',
         'Find.Job', 'Parks','Beauty','Roads','Housing','Night.Life', 'Minorities', 'Inmigrants', 'Gay', 'Safe','Colleges', 'Friends')

aux2 <- subset(des.cl1, variable %in% levels(des.cl1$variable)[1:31])
aux2$variable <- factor(aux2$variable)
aux2$var2 <- as.integer(aux2$variable)
colnames(aux2)[1] <- 'Clusters'

#,main='Mean Value Selected Variables Used in the K-means Cluster'
qplot(data = aux2, var2, value, color = Clusters,shape = Clusters,xlab = '', ylab = '',size = I(3)) +geom_line(size = I(.5)) + facet_wrap(~YEAR,nrow = 3) + theme(axis.text.x = element_text(angle = 90, size = I(15)), legend.position = 'bottom' ) + scale_x_discrete(breaks = 1:31, labels = lab) + scale_color_brewer(type='qual', palette='Paired')
@
\caption{Cluster mean points. Mean values for all the variables used to create the clusters in every year. \label{para}}
\end{figure}

>>>>

\begin{figure}[hbpt]
<<corplot, echo=FALSE, dependson=c('data'),cache=TRUE, warning = FALSE>>=
# With Census data we want to describe communities

@@

\begin{figure}[hbpt]
<<cluster.plot1, dependson='cluster',echo=FALSE,message=FALSE,warning=FALSE,warning=FALSE,fig.height=6.5>>=

des.cl1 %>% 
  spread(vars,value) %>% 
  select(Q25, QCE2, Q7E, Q3B, Q8D, Q8A, Q15AA, Q7L, Q9, Q3A, Q15AB, Q6A, Q3C, Q6, Q7I, Q7F, Q7K, Q8F, Q7M, Q7D, QCE1, Q7A, Q7B, Q7C, Q8C, Q8E, Q8B, Q7H, Q18, Q7G, Q24,YEAR,cl.id) %>% 
  rename( Family = Q25, Refer = QCE2, Perfect = Q7E, Children = Q3B, Leader = Q8D, Proud = Q8A, Lead.Int. = Q15AA, Talented = Q7L, Job = Q9, Meet.People = Q3A, `5year.ahead` = Q15AB, School = Q6A, Reputation = Q3C, `5year.ago` = Q6, Care = Q7I, Senior = Q7F, Economy = Q7K, Satisfaction = Q8F, Health = Q7M, Find.Job = Q7D, Parks = QCE1, 
Beauty = Q7A, Roads = Q7B, Housing = Q7C, Night.Life = Q8C, Minorities = Q8E, Inmigrants = Q8B, Gay = Q7H, Safe = Q18, Colleges = Q7G, Friends = Q24, Clusters = cl.id) %>% 
 gather(vars, value, -Clusters,-YEAR) %>% 
  ggplot(aes(x = vars, y = value, color = Clusters, shape = Clusters), size = I(3)) + labs(x = "", y = "") +  geom_point(size = I(2))  + geom_line(aes(group = Clusters)) + 
  facet_wrap(~YEAR, nrow = 3) + theme(axis.text.x = element_text(angle = 90, size = I(15)), legend.position = 'bottom' ) + scale_color_brewer(type='qual', palette='Paired')

@
\caption{Cluster mean points. Mean values for all the variables used to create the clusters in every year. \label{para}}
\end{figure}
